Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-14 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (4)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta} 
Indeed, we did not inform the impact the changing of computer setup or related issues. We thank you so much for this observation. Therefore we revised the text and included the following paragraph: "Note that the results presented here depend on the computer's processor and memory, the version of each tool (CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved. Additionally, any change from HOMER Pro to another simulation tool can influence the measured time to obtain results.".
\end{resposta}

>>>>

\begin{resposta} 
Indeed, we did not inform the impact of changing the computer setup or related issues. We thank the reviewer for this observation. We have revised our manuscript to include the following paragraph: ``Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved \textcolor{red}{what do you mean by the algorithm to be solved?}. Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.".
\end{resposta}
